### 2014-06-01 writing/S'14 paper/quantifiers.tex
Bracketing bug fix, wrote up quantifier examples.

\begin{table}\small\centering
\begin{tabular}{|ll|l|}
\hline
\textbf{(some $x$) mobile $\sqsupset$ (some $y$) mobile [s.t. $x\sqsupset y$]}&~&\textbf{(all $x$) French $\sqsubset$ (most $x$) European}		
\\\hline
(some dog) mobile	 $\sqsupset$  (some puppy) mobile	&&
(all puppy) French $\sqsubset$ (most puppy) European
\\
(some animal) mobile $\sqsupset$ (some cat) mobile&&
(all cat) French $\sqsubset$ (most cat) European 		\\

(some Asian) mobile $\sqsupset$ (some Thai) mobile&&(all hippo) French $\sqsubset$ (most hippo) European \\ ...&&...\\\hline
\end{tabular}
\caption{Sample datasets from two different templates.\label{examplesofdata}}
\end{table}

@@

\begin{table}\small\centering
\begin{tabular}{|l|ll|l|}\hline
Target dataset & Data evaluated   &  \textsc{subcl.-out} & \textsc{pair-out} \\\hline
\ii{(most $x$) bark $|$ (no $x$)} bark&target dataset only		&100\%&	93.6\%\\
\ii{(two $x$) bark \# (all $x$) bark}&target dataset only  			&100\%&	94.7\%\\
 \ii{(some $x$) bark $\natneg$ (no $x$) bark}&target dataset only 	&0\%&	0\%\\\hline
\end{tabular}
\caption{Test set accuracy.\label{resultstable}}
\end{table} % TODO: Replace

% TODO: Replace

\textsc{set-out:} In these experiments, I hold out the target dataset, training on none of it and testing on all of it, and additionally split each remaining dataset as in \textsc{all-split}. This setting is meant to test whether the model can generalize a broader reasoning pattern from one dataset to another---the model will still have seen other similar quantifier substitution datasets that differ from the target dataset only in which filler word is placed in the second argument position, as in row 5 in Table \ref{patterntable} above.

\textsc{pair-out:} In these experiments, I hold out all of the datasets that demonstrate the interaction between a particular pair of quantifiers. For the target dataset \ii{(most $x$) bark $|$ (no $x$) bark} in this setting, all examples with \ii{most} on one side and \ii{no} on the other, in either order, with or without negation or differing predicates, are held out from training. The remaining datasets are split as above.

These last three experiments have multiple sources of test data: some from the 15\% test portions of the datasets that were split, some from the target datasets, and some from any other similar datasets that were held out. In  Table \ref{resultstable}, I report results for each experiment on the entire test dataset, on the single target dataset, and on all of the held out datasets (i.e., the test data excluding the 15\% portions from the training datasets) in aggregate. This third figure is identical to the second for the \textsc{set-out} experiments, since the only held out dataset is the target dataset.

%\begin{table}\small\centering
%\begin{tabular}{|l|l|lll|}\hline
%Target dataset & Data evaluated   & \textsc{set-out} & \textsc{subcl.-out} & \textsc{pair-out} \\\hline
%\ii{(most $x$) bark $|$ (no $x$)} bark&target dataset only &100\%&100\%&0\%\\
%& all held out datasets                                 &(100\%) & 100\%& 49.4\%\\
%& all test data                                  &100\% & 99.9\%&85.7\%\\\hline
%\ii{(two $x$) bark \# (all $x$) bark}&target dataset only  &94.7\%&0\%&0\%\\
%& all held out datasets                                 &(94.7\%) & 70.0\%& 36.0\%\\
%& all test data                                  &98.9\% & 97.5\%&88.0\%\\\hline
% \ii{(some $x$) bark $\natneg$ (no $x$) bark}&target dataset only &2.6\%&0\%&0\%\\
%& all held out datasets                                 &(2.6\%) & 0\%& 17.6\%\\
%& all test data                                   &97.7\% & 93.7\%&83.9\%\\\hline
%\end{tabular}
%\caption{Test accuracy after 64 passes through the training data.\label{resultstable}}
%\end{table}

% The model did not converge well for any of these experiments: convergence can take hundreds or thousands of passes through the data, and the performance of the model at convergence  on test data was generally worse than its performance during the first hundred or so iterations. To sidestep this problem somewhat, I report results here for the models learned after 64 passes through the data. Even so, results are somewhat difficult to interpret: the performance on the test data fluctuates substantially between iterations, so a model that performs very poorly at iteration 64 may perform well at iteration 70. It is possible to stabilize the model by manipulating the hyperparameters away from their present tuned settings (raising minibatch size, shrinking model size, and increasing regularization, for example), but doing so consistently hurts performance.

Performance was perfect for at least some held out datasets in both the \textsc{set-out} and \textsc{subclass-out} settings, and near perfect for some in \textsc{pair-out}. Performance for one of the three target datasets---\ii{(some $x$) bark $\natneg$ (no $x$) bark}---was consistently poor across training settings. This poor performance is consistent across random initializations, and should be a target of further investigation. % TODO

>>>>

\begin{table}\small\centering
\begin{tabular}{|l|}
\hline
(most warthogs) walk $\natneg$ (not-most warthogs) walk\\
(most mammals) move \# (not-most (not turtles)) move\\
(most (not pets)) (not swim) $\sqsupset$ (not-most (not pets)) move\\
\hline
(no turtles) (not growl) $\|$ (no turtles) (not swim)\\
(no warthogs) swim $\sqsupset$ (no warthogs) move\\
(no warthogs) move $\sqsubset$ (no (not reptiles)) swim\\
\hline
\end{tabular}
\caption{Sample data from two different quantifier pairs.\label{examplesofdata}}
\end{table}

@@

\begin{table}\small\centering
\begin{tabular}{|l|l|}\hline
\textbf{Training configuration} & \textbf{Test accuracy}\\\hline
\textsc{all split}	&	TODO\% \\\hline
\textsc{pair no/no}	&	TODO\% \\
\textsc{pair two/$<$two}	&	TODO\% \\
\textsc{pair not-all/not-most}	&	TODO\% \\
\textsc{pair all/some}	&	TODO\% \\\hline
\end{tabular}

\caption{Quantifier experiment performance.\label{resultstable}}
\end{table} % TODO: Replace

% TODO: Define experimental setups
